High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales

### 2021-03-03 inst/manuscript/manuscript.Rmd
Edited start of discussion. Started committing figures

These results demonstrate our system's ability to create high resolution maps of the distribution and characteristics of cropland across a diverse and hard-to-map agricultural systems, at country-scales and at sub-annual to annual time steps. Our maps provide an updated and more granular view of the distribution and extent of arable croplands in Ghana, complementing existing national to regional land cover maps derived from moderate resolution sensors [@ESAESACCILAND; @hackmanNewLandcoverMaps2017; @XiongNominal30mCropland2017]. These earlier maps estimated that cropland covered `r round(4.62 / 23.86 * 100, 1)` [@XiongNominal30mCropland2017] to 32% [@hackmanNewLandcoverMaps2017] of Ghana's areas in the 2015, in contrast to our 2018 maps, in which cropland covers 16.1-23.2% of the mapped area (Table \ref{tab:mapaccuracy}), with sample-corrected estimates of `r segcipct[1]`-`r rfcipct[1]`%. Our findings suggests that Ghana's arable cropland is slightly less than previous estimates, although the difference may also be attributable to the earlier maps using a more expansive definition of cropland than ours (active to recently active fields).

>>>>

These results demonstrate a capability for mapping the characteristics of smallholder-dominated cropping systems at high spatial resolution, annual time steps, and national scales. The resulting maps provide an updated and more granular view of the distribution and extent of arable croplands in Ghana, complementing existing national to regional land cover maps derived from moderate resolution sensors [@ESAESACCILAND; @hackmanNewLandcoverMaps2017; @XiongNominal30mCropland2017]. This prior work found that cropland covered `r round(4.62 / 23.86 * 100, 1)` [@XiongNominal30mCropland2017] to 32% [@hackmanNewLandcoverMaps2017] of Ghana in 2015, whereas our 2018 maps have cropland cover of 16.1-23.2% (Table \ref{tab:mapaccuracy}), and our map reference sample-based estimates finds `r segcipct[1]`-`r rfcipct[1]`% cover. Our results thus suggest that Ghana's arable cropland is less than previously estimated, but the difference may be attributable to the earlier maps using a more expansive definition of cropland than we did (active to recently active fields).
